Category_Tables

### 2019-09-20 Analysis/Category_Tables.Rmd
Fix new column names

msig_cor = msig %>% group_by(Category) %>% summarise(Slope_Cor = cor(Count, Slope, "complete")) %>% arrange(Slope_Cor)

@@

msig_sum = msig %>% group_by(Category) %>% summarise(Min_Slope = min(Slope, na.rm = TRUE), Max_Slope = max(Slope, na.rm = TRUE), Mean_Slope = mean(Slope, na.rm = TRUE), Median_Slope = median(Slope, na.rm = TRUE), Min_Genes = min(Count), Max_Genes = max(Count), Mean_Genes = mean(Count), Median_Genes = median(Count), Total_Sets = n()) %>% arrange(Mean_Slope)

@@

kegg_string  = msig %>% filter(Category == "CP:KEGG") %>% dplyr::select(Count, Slope)

Slope_Sum = bind_rows(rand_string %>% mutate(Method = "Random"), kegg_string %>% dplyr::select(Count, Slope) %>% mutate(Method = "KEGG"))
```

>>>>

msig_cor = msig %>% group_by(Category) %>% summarise(Slope_Cor = cor(Num_Genes, Slope, "complete")) %>% arrange(Slope_Cor)

@@

msig_sum = msig %>% group_by(Category) %>% summarise(Min_Slope = min(Slope, na.rm = TRUE), Max_Slope = max(Slope, na.rm = TRUE), Mean_Slope = mean(Slope, na.rm = TRUE), Median_Slope = median(Slope, na.rm = TRUE), Min_Genes = min(Num_Genes), Max_Genes = max(Num_Genes), Mean_Genes = mean(Num_Genes), Median_Genes = median(Num_Genes), Total_Sets = n()) %>% arrange(Mean_Slope)

@@

kegg_string  = msig %>% filter(Category == "CP:KEGG") %>% dplyr::select(Num_Genes, Slope)

Slope_Sum = bind_rows(rand_string %>% mutate(Method = "Random"), kegg_string %>% dplyr::rename(Count=Num_Genes) %>% dplyr::select(Count, Slope) %>% mutate(Method = "KEGG"))
```
